### 2012-07-30 inst/examples/Reed.Rmd
Reed vs Clark, enforcing the self-sustaining principle #17

``` {r }
f <- BevHolt 
````

@@

``` {r noise}
z_g <- function() rlnorm(1,0, sigma_g)  # 1+(2*runif(1, 0,  1)-1) * sigma_g
````

>>>>

``` {r }
f <- function (x, h, p) 
{
      x <- max(0, x - h)
          A <- p[1]
          B <- p[2]
          sapply(x, function(x) {
            x <- max(0, x)
            max(0, A * x/(1 + B * x))
          })
}

````

@@

``` {r noise}
z_g <- function() 1 + rlnorm(1,0, sigma_g)  # 1+(2*runif(1, 0,  1)-1) * sigma_g
````
